Simulation Explorer

### 2018-06-01 inst/rmd/vis_sim.Rmd
Add some plotting functions and fix up vis_sim flexdashboard

---
title: "Simulation Explorer"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r global, include=FALSE}

library(plotly)
library(viridis)
library(shiny)
e <- new.env() # make a new environment to keep the global clean (rmarkdown::run wants to work in the global)
e$sim <- temp  # temp object (in global) created by vis_sim function
rm(temp)       # clean-up
e$ages <- e$sim$ages
e$years <- e$sim$years
e$vis_distribution <- "sp_N" %in% names(e$sim)

```

@@

```{r}
e$tot <- data.frame(Year = e$years, N = colSums(e$sim$N))
e$tot$text <- paste0("Year: ", e$tot$Year, "\nN: ", round(e$tot$N))
plot_ly(x = ~Year, y = ~N, text = ~text, hoverinfo = "text",
        type = "scatter", mode = "lines", data = e$tot) %>%
  layout(xaxis = list(rangeslider = list(type = "date")))
```

@@

```{r}

plot_ly(x = e$ages, y = e$years, z = e$sim$N, type = "surface") %>% 
  layout(
    scene = list(
      xaxis = list(title = "Age"),
      yaxis = list(title = "Year"),
      zaxis = list(title = "N")
    ))

```

@@

```{r}
plot_ly(x = e$ages, y = e$years, z = e$sim$Z, type = "surface") %>% 
  layout(
    scene = list(
      xaxis = list(title = "Age"),
      yaxis = list(title = "Year"),
      zaxis = list(title = "Z")
    ))
```

Distribution { `r if(!e$vis_distribution) ".hidden"`}
================================================================================

@@

```{r}

sliderInput("age", "Age", min = min(e$ages), max = max(e$ages), 
            value = 1, step = 1)
sliderInput("year", "Year", min = min(e$years), max = max(e$years), 
            value = 1, step = 1)
selectInput("type", "Type", choices = c("surface", "heatmap", "contour"), 
            selected = "surface")
checkboxInput("freez", label = "Free z limits?", value = FALSE)

```

@@

```{r, eval=e$vis_distribution}

e$d <- e$sim$sp_N
e$x <- sort(unique(e$d$x))
e$y <- sort(unique(e$d$y))
e$p <- plot_ly(x = e$x, y = e$y)

renderPlotly({
  e$z <- t(xtabs(N ~ x + y, subset = age == input$age & year == input$year, data = e$d))
  if (input$freez) {
    e$r <- range(e$z)
  } else {
    e$r <- range(e$d$N)
  }
  add_trace(e$p, z = e$z, type = input$type, zauto = input$freez, zmin = min(e$d$N), zmax = max(e$d$N)) %>%
    layout(autosize = TRUE,
           scene = list(zaxis = list(title = "N", range = e$r)))
})

```

>>>>

---
title: "Simulation Explorer"
output: flexdashboard::flex_dashboard
always_allow_html: yes
---

```{r setup, echo=FALSE}
library(plotly)
library(viridis)
knitr::opts_knit$set(root.dir = tmp$output_dir)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8)
```

```{r data, include=FALSE}
sim <- tmp$sim
```

@@

```{r}
plot_trend(sim)
```

@@

```{r}
plot_surface(sim, mat = "N")
```

@@

```{r}
plot_surface(sim, mat = "Z")
```

Distribution { `r if(!"sp_N" %in% names(sim)) ".hidden"`}
================================================================================

@@

```{r}
sliderInput("age", "Age", min = min(sim$ages), max = max(sim$ages), 
            value = 1, step = 1)
sliderInput("year", "Year", min = min(sim$years), max = max(sim$years), 
            value = 1, step = 1)
selectInput("type", "Type", choices = c("heatmap", "contour"), 
            selected = "contour")
selectInput("scale", "Scale", choices = c("natural", "log"), 
            selected = "natural")
```

@@

```{r, eval = "sp_N" %in% names(sim)}
renderPlotly({
  plot_distribution(sim, ages = input$age, year = input$year, type = input$type,
                    scale = input$scale)
})
```
